A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-27 manuscript.Rmd
rest of grammar

The above mentioned tools require much expertise that is beyond the traditional curriculum of researchers.
To aid researcher adopting these tools we rely on or have developed helpers that wrap more complicated (and powerful) tools.
These wrappers use standard tools but provide feedback for the user about what the computer does and what the user should do in layman's terms and are accessible from within R.
We hope this makes reproducibility tools more accessible by enabling beginner-level users to detect their systems state accurately and act correspondingly [@parasuramanAutomationHumanPerformance2018, Chapter 8: "Automation and Situation Awareness"].
These alternative tools are merely an assistance system, and as users get more and more comfortable, they can use the underlying tools directly to solve more complex problems.

Before we can start creating reproducible research projects, we need a computer with a working R Studio installation. 
Start R Studio and install the package [`repro`](https://github.com/aaronpeikert)[@R-repro] so that it can act as an assistance systems while you follow the tutorial:

@@

An example of the assistance that `repro` provides are the check functions.
They verify that you indeed have installed and setup the required pieces of software for this workflow (here, we use the double-colon operator to access functions from the `repro` namespace; we chose to do so to make clear which functions are native `repro` functions) :

@@

They detect the users' system state and explain if further action is needed.
Sometimes they ask the user to do something, for example, the following happens if you were a Windows user who does not have Git installed:

@@

You can prevent Git from accidentally committing files that you do not want to track with the `.gitignore` file.
You can add something to the `.gitignore` file directly or with this command:

@@

For Git to recognize changes to a given file, you have to stage and then commit these changes (this is the basic save action for a project snapshot).
The easiest way to do this is to use the RStudio Git pane.
Click on the empty box next to the file you want to stage, and when a tick appears, which means that the file is staged.
After you have staged all files you want, click on the commit button, explain in the commit message why you made those changes, and then click on commit.

@@

Now that you have created a project that is under version control, we continue with adding dynamic document generation.
Adynamic document has three elements:

1. Text in a natural language
2. Executable code 
3. Metadata

The text of an R Markdown is written in Markdown (see @xieMarkdownDefinitiveGuide2019 for technical details and @xieMarkdownCookbook2020 for practical guidance).
The following example serves to illustrate the Markdown syntax. 
It shows how to create a heading, a word in bold font, and a list of several items in Markdown:

@@

This type of markup for formatting, instead of the more visual approach of e.g. Microsoft Word, is compatible with many output formats and is easier to put under version control.
Some users might find it easier to activate the "Visual Editor" of R Studio (Ctrl + Shift + F4 or click on the icon that resembles drawing materials or a compass in the upper right corner of the R Markdown document) which features more graphical elements like a traditional word processor but still creates an R Markdown underneath with all of its flexibility.
The visual editor has the additional benefit of promoting best practices (for example, each sentence should be written on a newline, which eases tracking changes across versions).
Among other features, it eases the generation of citations and cross references.

Now that you are familiar with the basics of writing text in Markdown, we turn our attention to including code into the text.
Code is separated by three backticks (and the programming language in curly braces) like here:

@@

The results of your code are than dynamically inserted into the document.
Dynamically means that whenever you turn the R Markdown into its output format the code is executed again and if you changed something the results are updated.
The output document is than static, e.g. a pdf document, and can be shared wherever you like, e.g on a preprint server.
This static document is somewhat decoupled from the R Markdown and the rest of the code that did create it.
It is quite possible that several slightly different versions are therefore circulating.
We therefore recomend to connect the static document to the version control system by dynamically including the identifier of the identifier of the Git commit, called hash, in the document.
The `repro` package comes with the function `repro::current_hash()` for that purpose.
This document was created from the commit with the hash ``r repro::current_hash()``.

Now that you know how to write text and R code in an R Markdown, you need to know about metadata, like the title or the output format. Metadata are placed at the beginning of the document and are separated by three dashes from the document body; the following example is a full markdown document where the header is in lines 1--6.

@@

Most metadata fields are self-explanatory (like the author field). 
Sometimes, R package may extend the metadata fields for their own purposes.
Certain output formats may require specific  metadata. 
For example, the `rticles`-package that offers templates for authoring scientific manuscripts comes with extra fields that are described in the package documentation and offer extra options for flexible formatting of documents.
R Markdown has been extended to hundreds of document formats which are often highly configurable by their metadata.
The `repro` package uses the metadata for hints to make the research project reproducible.
Researchers should list all dependent resources of their research project in the metadata, that is, R scripts, data files, and external packages in the following format (see everything below the line *repro:*):

@@

This information makes internal dependencies to other files in the project and external dependencies to R packages explicit.
`repro` can use this information to infer a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
These two files together form the basis for consistency within a research project and consistency across different systems.
At this point, we would like to emphasize that a preqrequisite for reproducibility is that every step taken in an analysis can be automatically reproduced.
This means there must be no manual processing such as copy and pasting, manual modification of data files (e.g., manually removing observations or manually recoding variables). 
Ideally, all data preprocessing is well-documented and gathered in a separate R file, which is then called before a Markdown report is generated (that is, the preprocessing script is added in the metadata header under _scripts:_).
In everyday work, the simplest solution is to now call the function `repro::automate()` which both creates a Makefile and a Dockerfile from all R Markdown files in the project (all files with the ending `.Rmd`) based on the respective repro metadata entries.
Every time you change the `repro`-metadata, change the output format, or add a new R Markdown file to the project, the Makefile and Dockerfile are potentially outdated, and you should run `repro::automate()` to keep them up to date.
The function `repro::automate()` does not overwrite manual changes, and there is no harm in running it too often.
Other than the Makefile and the Dockerfile, which are created in the document root path, repro generates a few more files in the `.repro` directory (which we will explain in detail later), all of which you should add and commit to Git. <!--AB: why is this addition not automated? Feels strange given that this is our recommended best practice?!-->

When you or someone else who received your project want to reproduce it, they can ask repro to explain how this should be done:

@@

If you uncomfortable with using the terminal directly, you can sent the command to the terminal from within R:

@@

Some projects, however, are not as easy to make reproducible.
As explained above, `repro` is merely a simplified interface that guarantees a high level of reproducibility for simple projects.
These simplifications are possible because of two restrictions.
Users who ask themselves either "How can I install software that is not an R package in the Docker image?" or "How can I express complex dependencies between files, e.g. raw data turned into preprocessed data required by analysis?" need to be aware of these restriction and require a deeper understanding of the inner workings of `repro`.
All other users may safely skip this section and may return to it if they become limited by restriction.

The metadata the `repro::automate()` function relies on can only express dependencies R packages for the Dockerfile and only trivial dependencies (in the form of "file must exist") for the Makefile. 
The first limitation means that users must rely on software that is either already provided by the base Dockerimage "rocker/verse" or the R packages they list in the metadata.
Other software that users might need like other programming languages, not already installed LaTeX packages etc. have to be added manually.
We plan to add support for commonly used ways to install software beyond R packages via the metadata and `repro::automate()` e.g. for system libraries (via `apt` the Ubuntu package manager), LaTeX packages (via `tlmgr` the Tex Live package manager), python packages (via `pip` the python package manager).
The second limitation is about dependencies.
Make can represent complex dependencies like in this example: A depends on B, which in turn depends on C and D.
If B is missing in this example, Make would know how to recreate it from C and D.
These dependencies and especially how these dependencies should be resolved are difficult to represent in the metadata.
Users therefore have to either "flatten" the dependency structure, by simply stating that A depends on B, C and D therefore leaving out important information or express the dependencies directly within the Makefile.

The following section explains how to overcome these limitation while still relying on the automatons afforded by `repro`.
Lifting these restrictions requires the user to interact more directly with Make or Docker.
To satisfy more complicated requirements users need to understand how repro utilizes Make and Docker internally.

Let us have a closer look at the command for reproducing a repro project: `make docker && make -B DOCKER=TRUE`; it consists of two processing steps.
First it recreates the virtual software environment (Docker) and then it executes computational recipes in the virtual software environment (Make).
The first step is done by the command `make docker`.
The command `make docker` will trigger Make to build the target called `docker`.
The recipe for this target builds an image from the Dockerfile of the repository.
The `&&` concatenates both commands and only runs the second command if the first was successful.
Therefore, the computational steps are only executed when the software environment is set up.
The second step executes the actual reproduction and is again a call to Make in the form of `make -B DOCKER=TRUE` with three noteworthy parts.
First, a call to `make` without any explicit target will build the Make target `all`.
Second, the flag `-B` means that Make will consider all dependencies as outdated and hence will rebuild everything.
Third, repro constructs Make targets so that if you supply `DOCKER=TRUE` they are executed within the Docker image of the project.

@@

Users can have full control over the software installed within the image of the project.
`repro` creates three Dockerfiles inside the `.repro` directory.
The file `.repro/Dockerfile_base` contains information about the base image on which all the remaining software is installed.
By default we rely on the "verse" images provided by the Rocker project [@boettigerIntroductionRockerDocker2017].
These contain (among other software) the packages `tidyverse`, `rmarkdown` and a complete LaTeX installation, which makes these images ideal for the creation of scientific manuscripts.
Users can choose which R version they want to have inside the container by changing the version number in line 1 to the desired R version number.
By default the R version corresponds to the locally installed version on which `repro::automate()` was called the first time.
The build date is used to install packages in the version which was available on CRAN on this specific date and can also be changed, by default this date is set to the date on which `repro::automate()` was called the first time. 
This way, the call to the automate function virtually freezes the R environment to the state it was called the first time inside the container. 
Below, you see the Docker base file we used to create this manuscript:

@@

The file `.repro/Dockerfile_manual` is empty by default and can be used to add further dependencies outside of R, like system libraries or external software. 
Remember, the software environment of the Docker image is completely separate from software installed on your computer.
This separation is excellent for reproducibility, but requires you to install software on an operating system that may not be familiar to you.
The images supplied by [@boettigerIntroductionRockerDocker2017] are based on Ubuntu, and hence software has to be installed in a way that is compatible with Ubuntu.
The most convenient way to install software on Ubuntu is through its package manager `apt`.
The following snipped installs Python.
If added to `.repro/Dockerfile_manual` the Docker image will have Python installed.

@@

With this approach, users of `repro` can not only build complex software environments but they can also implement complex file dependencies.
The standard `repro` metadata only makes sure that all dependencies are available but does not allow you to specify custom recipes for them in the metadata.
If you can formulate the creation of dependencies in terms of computational steps, e.g. the file `data/clean.csv` is created from `data/raw.csv` by script `R/preprocess.R`, you should include these in the Makefile.
The Makefile that `repro` creates is only an template and you are free to change it.
However, make sure to never remove the following two lines:

@@

The file `.repro/Makefile_Rmds` contains the automatically generated targets from `repro::automate()` for the R Markdown files.
This file should not be altered manually.
If you are not satisfied with the automatically generated target than simply provide an alternative target in the main `Makefile`.
Targets in the main `Makefile` take precedent.

The file `.repro/Makefile_Docker` does again contain a rather complicated template which you could but usually should not modify.
This Makefile coordinates the interplay between Make and Docker and contains targets for building (with `make docker`) and saving (with `make save-docker`) the Docker image.
Additionally, it provides facilities to execute commands within the container.
If you write computational recipe for a target it will be by default evaluated using the locally installed software.
To instead evaluate commands inside the Docker image, you should wrap them in `$(RUN1) command $(RUN2)`, like in this example, which is identical to the first Make example we gave above except for the addition of `$(RUN1)` and `$(RUN2)` in l. 2:
```bash
simulated_data.csv: R/simulate.R
  $(RUN1) Rscript -e 'source("R/simulate.R")' $(RUN1)
```

@@

Defining the research questions and planning data analysis before observing the research outcomes is called preregistration [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a priori planned analyses from those conducted unplanned and post hoc.
For a priori planned analyses, preregistration should reduce "researcher degrees of freedom" therefore, the number of decisions researcher can make that could unduly influence the results.
Preregistrations, however, have a problem.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration is comprehensive and specific enough is to use preregistration templates [like @bowmanOSFPreregTemplate2020].
The structure these templates provide can more effectively reduce researchers degrees of freedom than an unstructured approach [@bakkerEnsuringQualitySpecificity2020].
Nevertheless, these templates can not remove researchers' degrees of freedom because it is impossible to verbally describe every detail of an analysis for all but the most straightforward analysis.

Our proposed solution is simple:
Instead of describing the analysis, you write the code to conduct the analysis before you gather data.
We term this writing and publishing code before data collection *preregistration as code (PAC)*.
PAC has the potential to all but eliminates researchers degrees of freedom that standard preregistration despite the best efforts afford.

@@

We believe, however, that combining ideas from reproducibility and preregistration can turn this "neat" idea into a tool with tangible benefits for the research community.

@@

Second, although it has been almost a decade since @steegenMeasuringCrowdAgain2014 have preregistered their code, the idea of publishing code before analyzing data has gained not much traction.
This could change when combining the here proposed workflow and PAC.
We want to extend PAC from preregistering code to preregistering *the whole manuscript as a dynamic document*.
The idea is as follows:
For a PAC, researchers write a reproducible, dynamically generated manuscript including the sections Introduction, Methods, and Results (or similar) _before_ they gather empirical data.
In this document, the results are initially based on simulated data that mimics the expected output.

Writing a preregistration in form of a research article has the advantage that researchers already have great expertise in writing a scientific manuscript.
It follows that for preregistrations they should stick to widely accepted standards of scientific writing [e.g. @apa7].
We have already explained the need for reproducibility standards in the process of writing such manuscript and it is therefore only natural to extend these arguments to preregistration.

@@

We believe that pairing PAC with the here presented workflow offers five advantages over classical preregistration.
First, a PAC removes any ambiguity regarding the translation of a verbal analysis plan into code.
Second, while being rigorous, it offers the flexibility to incorporate data-dependent decisions if they can be formulated as code.
Researchers can, for example, formulate conditions under which they prefer one analysis type over the other.
For example, if distributional assumptions are not met, the code may branch out to employ robust methods; or, an analysis may perform automated variable selection mechanisms before running the final model.
Third, a PAC is more comprehensive by design because its completeness can be empirically checked with simulated data.
We believe it is easier with PAC to detect missing steps or ambiguous decisions.
Because of its strict structure, PAC can therefore more effectively minimize researchers degrees of freedom than a standard preregistration [@bakkerEnsuringQualitySpecificity2020].
Fourth, deviations from the preregistration are visible because they are reflected in changes to the code, which are managed and tracked with version control.
Fifth, the preregistration is merely a development stage of the final manuscript, thus sparing authors from writing, and editors and reviewers from evaluating two separate documents.

@@

When leaving meta-scientific benefits aside, a preregistration is a tool for planning a study.
To use PAC for study planning, we suggest that researchers write a dynamically generated manuscript including the sections Introduction, Methods, and Results (or similar) _before_ they gather empirical data.
To that end, they should borrow from widely employed standards for writing an empirical manuscript [e.g. @apa7].
Then they should translate their method section into executable computer code and simulate data that has the same structure as the data they expect to obtain from their experiments.

We consider three domains where this procedure can help planning a study.
First, the plan should be comprehensive, that is, researchers need to state the research question and describe the study design and analysis in detail.
Second, the plan should be effective, meaning that the researchers can reasonably expect it to answer the research question at hand.
Third, the plan should be efficient; the plan should only require the necessary amount of resources.

@@

Describing the preregistration in form of a journal article requires authors to follow the same standards that also ensure that research articles are comprehensive enough to replicate the described study.
One particular advantage is the foundation in existing literature where the introduction and theoretical background provide the basis for the studies' design.
Nevertheless, it can be fruitful to consult preregistration templates because of their strong focus on formulating a comprehensive methods section.

Another factor that ensures a comprehensive plan is writing the analysis based on simulated data.
While relatively uncommon for an empirical research project, we argue that simulating data offers various benefits in the planning phase of a study.
When simulating data, researchers have to think about and address data-analytic problems on a conceptual level before making an effort to acquire data [@axelrodAdvancingArtSimulation1997].
It also affords researchers with a simple technical check whether the analysis code runs without failure [@braiekTestingMachineLearning2020] (for example, does the code work with missing values, extreme outliers, etc.).
Writing incomplete code is technically impossible, or at least researchers would notice if they, e.g. forgot to aggregate the data, and so forth.

@@

With simulated data, researchers can check if the analysis recovers the known parameters of the simulation.
When an analysis fails to recover the correct values in idealized conditions with big samples, researchers should not expect this analysis to be effective under realistic conditions.
Because the simulation captures the researchers' expectations about the real world, it is the best way to assess the effectiveness of the analysis without actually gathering the data.

@@

```{r, eval=FALSE}
planned_analyis <- function(data){
  # 1. preprocess e.g. with `rowMeans(data)`
  # 2. conduct analysis e.g. with `t.test()`
  # 3. `return(results)`
}
```

@@

```{r, eval=FALSE}
simulate_data <- function(n, effect_size){
  # 1. warn users that the results are mocked
  # 2. draw `n` samples with `effect_size`
  # 3. format and return in expected data format
}
```

@@

When the researchers are satisfied with the function `planned_analysis()`, they can think about how they would like to report the analysis results via tables, plots, and text.
The implementation of this reporting should be in the function `report_analysis()`.

```{r, eval=FALSE}
report_results <- function(results){
  # 1. create markdown tables from results
  # 2. conditionally interpret results e.g. if(p < .025)"Result is significant."
  # (optional) visualize results
  # 3. return results section formatted in markdown
}
```

@@

To summarize, researchers write three functions, `planned_analysis()`, `simulate_data()`, and `report_analysis()` and embed these into a manuscript that serves as preregistration.
After they gathered the actual data, they replace the simulated data, render the dynamic manuscript (therefore run `planned_analysis()`) and write the discussion.

@@

The interested reader can find the example rendered with actual data in the [online supplementary material](this link does not work) and can view the changes we made since preregistering it on this [GitHub page](this link does not work).

>>>>

The above mentioned tools require expertise that is beyond the traditional curriculum of researchers.
To aid researchers adopting these tools we rely on and have developed helpers that wrap more complicated (and powerful) tools.
These helpers wrap standard tools but provide feedback about what the computer does and what the user should do in layman's terms and are accessible from within R.
These alternative tools are merely an assistance system, and as users get more and more comfortable, they can use the underlying tools directly to solve more complex problems.

Before we can start creating reproducible research projects, we need a computer with a working R Studio installation. 
Start R Studio and install the package [`repro`](https://github.com/aaronpeikert)[@R-repro] so it can assist you following the tutorial:

@@

An example of the assistance that `repro` provides are the check functions.
They verify that you indeed have installed and setup the required pieces of software for this workflow (we use the double-colon operator to access functions from the `repro` namespace to make clear which functions are native `repro` functions):

@@

They detect the users' system state and explain if further action is needed.
For example, the following happens if you were a Windows user who does not have Git installed:

@@

You can prevent Git from accidentally committing files that you do not want to track with the `.gitignore` file.
You can edit the `.gitignore` file directly or with this command:

@@

For Git to recognize changes to a given file, you have to stage and then commit these changes (this is the basic save action for a project snapshot).
The easiest way to do this is to use the RStudio Git pane.
Click on the empty box next to the file you want to stage, and when a tick appears, which means that the file is staged.
After you have staged all files you would like to, click on the commit button, explain in the commit message why you made those changes, and then click on commit.
<!---
Maybe first click on the commit button and then stage, because in the bigger window you can browse the changes.
-->

@@

Now that you have created a project that is under version control, we continue with adding dynamic document generation.
A dynamic document has three elements:

1. Text
2. Executable code
3. Metadata

The text of an R Markdown is formatted by Markdown (see @xieMarkdownDefinitiveGuide2019 for technical details and @xieMarkdownCookbook2020 for practical guidance).
The following example serves to illustrate the Markdown syntax.
It shows how to create a heading, a word in bold font, and a list of several items in Markdown:

@@

This type of markup for formatting, instead of the more visual approach of e.g. Microsoft Word, is compatible with many output formats and is easier to put under version control.
Some users might find it easier to activate the "Visual Editor" of R Studio (Ctrl + Shift + F4 or click on the icon that resembles drawing materials or a compass in the upper right corner of the R Markdown document) which features more graphical elements like a traditional word processor but still creates an R Markdown underneath with all of its flexibility.
The visual editor has the additional benefit of promoting best practices (for example, each sentence should be written on a new line, which eases tracking changes across versions).
Among other features, it eases the generation of citations and cross references.

Now that you are familiar with the basics of writing text in Markdown, we turn our attention to including code into the text.
Code is separated by three backticks (and the programming language in curly braces):

@@

The results of your code are dynamically inserted into the document.
Dynamically means that whenever you turn the R Markdown into its output format the code is executed again and if you changed something the results are updated.
<!---
you did not explain how to knit and to choose an output format
-->
The output document is then static, e.g. a pdf document, and can be shared wherever you like, e.g on a preprint server.
This static document is somewhat decoupled from the R Markdown and the rest of the code that did create it.
It is quite possible that several slightly different versions are therefore circulating.
We therefore recommend to connect the static document to the version control system by dynamically including the identifier of the Git commit, called hash, in the document.
The `repro` package comes with the function `repro::current_hash()` for that purpose.
This document was created from the commit with the hash ``r repro::current_hash()``.

Now that you know how to write text and R code in an R Markdown, you need to know about metadata, like the title or the output format. Metadata are placed at the beginning of the document and are separated by three dashes from the document body. The following example is a full markdown document where the the metadata (the "header") is in lines 1--6.

@@

Most metadata fields are self-explanatory (like the author field). 
Sometimes, R packages may extend the metadata fields for their own purposes.
Certain output formats may require specific  metadata. 
For example, the `rticles`-package, which offers templates for authoring scientific manuscripts, comes with extra fields that are described in the package documentation and offer extra options for flexible formatting of documents.
R Markdown has been extended to hundreds of document formats which are often highly configurable by their metadata.
The `repro` package uses the metadata for hints to make the research project reproducible.
Researchers should list all dependent resources of their research project in the metadata, that is, R scripts, data files, and external packages, in the following format (see everything below the line *repro:*):

@@

This information makes internal dependencies to other files in the project and external dependencies to R packages explicit.
`repro` can use this information to infer a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
These two files together form the basis for consistency within a research project and consistency across different systems.
<!---
What is consistency?
-->
At this point, we would like to emphasize that a prerequisite for reproducibility is that every step taken in an analysis can be **automatically** reproduced.
This means there must be no manual processing such as copy and pasting, manual modification of data files (e.g., manually removing observations or manually recoding variables). 
Ideally, all data preprocessing is well-documented and gathered in a separate R file, which is then called before a Markdown report is generated (that is, the preprocessing script is added in the metadata header under _scripts:_).

In everyday work, the simplest solution is to now call the function `repro::automate()` which creates a Makefile and a Dockerfile from all R Markdown files in the project based on the respective repro metadata entries.
Every time you change the `repro`-metadata, change the output format, or add a new R Markdown file to the project, the Makefile and Dockerfile are potentially outdated, and you should run `repro::automate()` to keep them up to date.
The function `repro::automate()` does not overwrite manual changes, and there is no harm in running it too often.
Other than the Makefile and the Dockerfile, which are created in the document root path, repro generates a few more files in the `.repro` directory (which we will explain in detail later), all of which you should add and commit to Git. <!--AB: why is this addition not automated? Feels strange given that this is our recommended best practice?!-->

When you or someone else who received your project would like to reproduce it, they can ask repro to explain how this should be done:

@@

If you feel uncomfortable using the terminal directly, you can sent the command to the terminal from within R:

@@

Some projects, however, are not so easy to make reproducible.
As explained above, `repro` is merely a simplified interface that guarantees a high level of reproducibility for simple projects.
These simplifications are possible because of two restrictions.
Users who ask themselves either "How can I install software that is not an R package in the Docker image?" or "How can I express complex dependencies between files, e.g. raw data turned into preprocessed data required by analysis?" need to be aware of these restriction and require a deeper understanding of the inner workings of `repro`.
All other users may safely skip this section and return if they need to.

The metadata the `repro::automate()` function relies on can only express R packages as dependencies for the Dockerfile and only trivial dependencies (in the form of "file must exist") for the Makefile. 
The first limitation means that users must rely on software that is either already provided by the base Dockerimage "rocker/verse" or the R packages they list in the metadata.
Other software that users might need like other programming languages and not preinstalled LaTeX packages have to be added manually.
We plan to add support for commonly used ways to install software beyond R packages, e.g. for system libraries (via the Ubuntu package manager `apt`), LaTeX packages (via the Tex Live package manager `tlmgr`), and python packages (via the python package manager `pip`).
The second limitation is about dependencies.
Make can represent complex dependencies like in this example: A depends on B, which in turn depends on C and D.
If B is missing in this example, Make would know how to recreate it from C and D.
These dependencies and especially how these dependencies should be resolved are difficult to represent in the metadata.
Users therefore have to either "flatten" the dependency structure by simply stating that A depends on B, C and D, thereby leaving out important information, or express the dependencies directly within the Makefile.

The following section explains how to overcome these limitations while still relying on the automations provided by `repro`.
Lifting these limitations requires the user to interact more directly with Make or Docker.
To satisfy more complicated requirements users need to understand how repro utilizes Make and Docker internally.
<!-- I am pretty shure you are saying that users should satisfy more complicated requirements ^^ -->

Let us have a closer look at the command for reproducing a repro project: `make docker && make -B DOCKER=TRUE`. It consists of two processing steps:
First it recreates the virtual software environment (Docker) and then it executes computational recipes in the virtual software environment (Make).
The first step is done by the command `make docker`, it will trigger Make to build the target called `docker`.
The recipe for this target builds an image from the Dockerfile of the repository.
The `&&` concatenates both commands and only runs the second command if the first was successful.
Therefore, the computational steps are only executed when the software environment is set up.
The second step executes the actual reproduction and is again a call to Make in the form of `make -B DOCKER=TRUE` with three noteworthy parts.
First, a call to `make` without any explicit target will build the Make target `all`.
Second, the flag `-B` means that Make will consider all dependencies as outdated and hence will rebuild everything.
Third, repro constructs Make targets so that if you supply `DOCKER=TRUE` they are executed within the Docker image of the project.

@@

Users can have full control over the software installed within the image of the project.
`repro` creates three Dockerfiles inside the `.repro` directory.
The file `.repro/Dockerfile_base` contains information about the base image on which all the remaining software is installed.
By default we rely on the "verse" images provided by the Rocker project [@boettigerIntroductionRockerDocker2017].
These contain (among other software) the packages `tidyverse`, `rmarkdown` and a complete LaTeX installation, which makes these images ideal for the creation of scientific manuscripts.
Users can choose which R version they want to have inside the container by changing the version number in line 1 to the desired R version number.
By default the R version corresponds to the locally installed version on which `repro::automate()` was called the first time.
The build date is used to install packages in the version available on CRAN on this specific date and can also be changed, by default it is set to the date on which `repro::automate()` was called the first time. 
This way, the call to the automate function virtually freezes the R environment to the state it was called the first time inside the container. 
Below, you see the Docker base file we used to create this manuscript:

@@

The file `.repro/Dockerfile_manual` is empty by default and can be used to add further dependencies outside of R, like system libraries or external software. 
Remember, the software environment of the Docker image is completely separate from software installed on your computer.
This separation is excellent for reproducibility, but requires you to install software on an operating system that may not be familiar to you.
The images supplied by [@boettigerIntroductionRockerDocker2017] are based on Ubuntu, and hence software has to be installed in a way that is compatible with Ubuntu.
The most convenient way to install software on Ubuntu is through its package manager `apt`.
If the following snipped is added to `.repro/Dockerfile_manual` the Docker image will have Python installed.

@@

With this approach, users of `repro` can not only build complex software environments but they can also implement complex file dependencies.
The standard `repro` metadata only makes sure that all dependencies are available but does not allow you to specify custom recipes for them in the metadata.
If you can formulate the creation of dependencies in terms of computational steps, e.g. the file `data/clean.csv` is created from `data/raw.csv` by script `R/preprocess.R`, you should include these in the Makefile.
The Makefile that `repro` creates is only a template and you are free to change it.
However, make sure to never remove the following two lines:

@@

The file `.repro/Makefile_Rmds` contains the automatically generated targets from `repro::automate()` for the R Markdown files.
This file should not be altered manually.
If you are not satisfied with the automatically generated target simply provide an alternative target in the main `Makefile`.
Targets in the main `Makefile` take precedent.

The file `.repro/Makefile_Docker` does again contain a rather complicated template which you could but usually should not modify.
This Makefile coordinates the interplay between Make and Docker and contains targets for building (with `make docker`) and saving (with `make save-docker`) the Docker image.
Additionally, it provides facilities to execute commands within the container.
If you write a computational recipe for a target it will be by default evaluated using the locally installed software.
To instead evaluate commands inside the Docker image, you should wrap them in `$(RUN1) command $(RUN2)`, like in this example, which is identical to the first Make example we gave above except for the addition of `$(RUN1)` and `$(RUN2)` in l. 2:
```bash
simulated_data.csv: R/simulate.R
  $(RUN1) Rscript -e 'source("R/simulate.R")' $(RUN1)
```

@@

Defining the research questions and planning data analysis before observing the research outcomes is called preregistration [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a priori planned analyses from those conducted unplanned and post hoc.
For a priori planned analyses, preregistration should reduce "researcher degrees of freedom", the number of decisions researchers can make that could influence the results.
However, some problems described in the literature make it questionable whether preregistration can achieve its goals.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration is comprehensive and specific enough is to use preregistration templates [like @bowmanOSFPreregTemplate2020].
The structure these templates provide can more effectively reduce researcher degrees of freedom than an unstructured approach [@bakkerEnsuringQualitySpecificity2020].
Nevertheless, these templates can not remove all researcher degrees of freedom because it is impossible to verbally describe every detail of an analysis for all but the most straightforward analysis.

Our proposed solution is simple:
Instead of describing the analysis, you write and publish the code to conduct the analysis before you gather data.
<!-- I am not shure if it is good to directly talk to the reader in this form -->
We term this *preregistration as code (PAC)*.
PAC has the potential to eliminate all researcher degrees of freedom, even those standard preregistration can not eliminate.

@@

We believe, however, that combining ideas from reproducibility and preregistration can turn this idea into a tool with tangible benefits for the research community.

@@

Second, although it has been almost a decade since @steegenMeasuringCrowdAgain2014 have preregistered their code, the idea of publishing code before analyzing data has gained not much traction.
<!-- This is not a reason why PAC and reproducibility are related -->
This could change when combining the here proposed workflow and PAC.
We want to extend PAC from preregistering code to preregistering *the whole manuscript as a dynamic document*.
The idea is as follows:
For a PAC, researchers write a reproducible, dynamically generated manuscript including the sections Introduction, Methods, and Results (or similar) _before_ they gather empirical data.
In this document, the results are initially based on simulated data that mimics the expected output.

Writing a preregistration in form of a research article has the advantage that researchers already have great expertise in writing a scientific manuscript.
It follows that for preregistrations they should stick to widely accepted standards of scientific writing [e.g. @apa7].
We have already explained the need for reproducibility standards in the process of writing such manuscripts and it is therefore only natural to extend these arguments to preregistration.

@@

We believe that pairing PAC with the here presented workflow offers five advantages over classical preregistration.
First, a PAC removes any ambiguity regarding the translation of a verbal analysis plan into code.
Second, while being rigorous, it offers the flexibility to incorporate data-dependent decisions if they can be formulated as code.
Researchers can, for example, formulate conditions under which they prefer one analysis type over the other.
For example, if distributional assumptions are not met, the code may branch out to employ robust methods or an analysis may perform automated variable selection mechanisms before running the final model.
Third, a PAC is more comprehensive by design because its completeness can be empirically checked with simulated data.
We believe PAC reveals missing steps or ambiguous decisions. 
It can therefore more effectively minimize researchers degrees of freedom than a standard preregistration [@bakkerEnsuringQualitySpecificity2020].
Fourth, deviations from the preregistration are visible because they are reflected in changes to the code, which are managed and tracked with version control.
Fifth, the preregistration is merely a development stage of the final manuscript, thus sparing authors from writing, and editors and reviewers from evaluating two separate documents.

@@

Leaving meta-scientific benefits aside, a preregistration is also a tool for study planning.
To use PAC for study planning, we suggest that researchers write a dynamically generated manuscript including the sections Introduction, Methods, and Results (or similar) _before_ they gather empirical data.
To that end, they should borrow from widely employed standards for writing an empirical manuscript [e.g. @apa7].
Then they should translate their method section into executable computer code and simulate data that has the same structure as the data they expect to obtain from their experiments.

We consider three domains where this procedure can help planning a study.
First, the plan should be comprehensive, that is, researchers need to state the research question and describe the study design and analysis in detail.
Second, the plan should be effective, meaning that the researchers can reasonably expect it to answer the research question at hand.
Third, the plan should be efficient; it should only require the necessary amount of resources.

@@

Describing the preregistration in form of a journal article requires authors to follow the same standards that also ensure that research articles are comprehensive enough to replicate the described study.
<!-- I dont understand this sentence -->
One particular advantage is the foundation in existing literature where the introduction and theoretical background provide the basis for the studies' design.
Nevertheless, it can be fruitful to consult preregistration templates because of their strong focus on formulating a comprehensive methods section.

Another factor that ensures a comprehensive plan is writing the analysis based on simulated data.
While relatively uncommon for an empirical research project, we argue that simulating data offers various benefits in the planning phase of a study.
When simulating data, researchers have to think about and address data-analytic problems on a conceptual level before making an effort to acquire data [@axelrodAdvancingArtSimulation1997].
It also affords researchers with a simple technical check whether the analysis code runs without failure [@braiekTestingMachineLearning2020] (for example, does the code work with missing values, extreme outliers, etc.).
Writing incomplete code is technically impossible, or at least researchers would notice if something is omitted (e.g. if they forgot to aggregate the data).

@@

With simulated data, researchers can check if the analysis recovers the known parameters of the simulation.
When an analysis fails to recover the correct values in idealized conditions with big samples, researchers should not expect this analysis to be effective under realistic conditions.
Because the simulation captures the researchers' expectations about the real world, it is the best way to assess the effectiveness of the analysis without actually gathering the data.
<!-- I would maybe say something about why the simulated data captures researchers expectations. I think for most people data simulation is a novel topic, and even more so the idea that complicated assumptions about the real world (skewness, factor structure of a test, violated measurement invariance) can be incorporated into the simulation -->

@@

```{r, eval=FALSE}
planned_analyis <- function(data){
  # 1. preprocess e.g. with `rowMeans(data)`
  # 2. conduct analysis e.g. with `t.test()`
  # 3. return the results
}
```

@@

```{r, eval=FALSE}
simulate_data <- function(n, effect_size, measurement_error, etc.){
  # 1. warn users that the results are mocked
  # 2. draw `n` samples with `effect_size`
  # 3. Further assumptions can be passed to this function, like measurement error, skewness, etc.
  # 4. format and return in expected data format
}
```

@@

When the researchers are satisfied with the function `planned_analysis()`, they can think about how they would like to report the analysis results via tables, plots, and text.
The implementation of this reporting should be in the function `report_analysis()`.
<!-- Inconsistent naming of the function report_analysis() !! -->

```{r, eval=FALSE}
report_results <- function(results){
  # 1. create markdown tables from results
  # 2. conditionally interpret results e.g. if(p < .025)"Result is significant."
  # 3. visualize results
  # 4. return results section formatted in markdown
}
```

@@

To summarize, researchers write three functions, `planned_analysis()`, `simulate_data()`, and `report_analysis()` and embed these into a manuscript that serves as a preregistration.
After they gathered the actual data, they replace the simulated data, render the dynamic manuscript (therefore run `planned_analysis()` on the actual data) and write the discussion.

@@

The interested reader can find the example rendered as a pdf file with actual data in the [online supplementary material](this link does not work) and can view the changes we made since preregistering it on this [GitHub page](this link does not work).
<!-- I would show the rendered PDF (as long as it is shorter than one page) -->
